---
title: "R Notebook"
output: html_notebook
---

Code for generating figures for supplementary 

```{r}
library(tidyverse)
library(latex2exp)
#library(plotly)
source("plot_utils.R")

rename_methods <- function(df) {
  return(mutate(df,method = factor(recode(method,
                                bc = "DR",
                                conf = "TCR",
                                pl = "PL"),
                levels = rev(c(
                           "DR",
                           "PL",
                           "TCR")))))
}
```

# Vary p, q, gamma but fix zeta for m = 0 and m = 0.25 [rerunning at 100 sim]

```{r}
results_folder <- "results/paper/vary_p_q_gamma_fix_zeta/"
var_param <- quo(p)
img_folder <- "img/vary_p_q_gamma_fix_zeta_"


fl = list.files(results_folder, pattern = ".results.")
setwd(results_folder)
results <- bind_rows(lapply(fl, readRDS)) %>% rename_methods()
```


> uncorrelated lasso

```{r}
results %>%
  dplyr::filter(m == 0, algorithm == "LASSO") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m0.pdf"), width =5, height = 4)
```
> uncorrelated Rf

```{r}
results %>%
  dplyr::filter(m == 0, algorithm == "RF") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m0.pdf"), width =5, height = 4)
```

> correlated LASSO

```{r}
results %>%
  dplyr::filter(m == 0.25, algorithm == "LASSO") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m25.pdf"), width =5, height = 4)
```


> correlated RF

```{r}
results %>%
  dplyr::filter(m == 0.25, algorithm == "RF") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m25.pdf"), width =5, height = 4)
```





# Vary p, q, gamma and zeta but zeta at a different ratio than gamma [100 sim, running]

```{r}
results_folder <- "results/paper/vary_p_q_gamma_zeta5/"
var_param <- quo(p)
img_folder <- "img/vary_p_q_zeta5_"


fl = list.files(results_folder, pattern = ".results.")
setwd(results_folder)
results <- bind_rows(lapply(fl, readRDS)) %>% rename_methods()

```


> correlated lasso

```{r}
results %>%
  dplyr::filter(m == 0.25, algorithm == "LASSO") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m25.pdf"), width =5, height = 4)
```

> correlated rf

```{r}
results %>%
  dplyr::filter(m == 0.25, algorithm == "RF") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m25.pdf"), width =5, height = 4)
```

> uncorrelated LASSO

```{r}
results %>%
  dplyr::filter(m == 0, algorithm == "LASSO") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())
```
> uncorrelated RF

```{r}
results %>%
  dplyr::filter(m == 0, algorithm == "RF") %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())
```



# Vary p, q, gamma and zeta at equal ratios [no RF, 500 sim]
Note that TCR does well at high p since zeta is small there

```{r}
results_folder <- "results/paper/vary_p_q_gamma_zeta/"
var_param <- quo(p)
img_folder <- "img/vary_p_q_gamma_zeta_"


fl = list.files(results_folder, pattern = ".results.")
setwd(results_folder)
results <- bind_rows(lapply(fl, readRDS)) %>% rename_methods()
```


> correlated

```{r}
results %>%
  dplyr::filter(m == 0.25) %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())

#ggsave(glue::glue(img_folder, "m25.pdf"), width =5, height = 4)
```
> uncorrelated

```{r}
results %>%
  dplyr::filter(m == 0) %>%
  dplyr::group_by(!! var_param, method) %>%
  dplyr::filter(! (method %in% c("Oracle DR"))) %>%
  dplyr::summarise(
    mmse = mean(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()),
  ) %>%
  ggplot(aes(x = !! var_param, y = mmse, color = method)) +
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = low, ymax = high), width = 10) +
  ylab(TeX("$E\\[(\\nu(V) - \\hat{\\nu}(V))^2\\]$")) +
 scale_x_continuous(breaks = seq(50, 450, 50), minor_breaks = seq(50, 450, 50)) +
 xlab(TeX("$d_v$")) +
  scale_color_manual(values = cbPalette[1:4])+
  theme_bw(base_size = 21) +
   theme(legend.position = c(0.8, 0.24), legend.title = element_blank())
```
