---
title: "Visualization Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
source("regression_functions.R")
source("utils.R")
```

This notebook visualizes the simulation results in 
```{r}
results_folder <- "results/mu_sigmoid/propa3/train500_ext/"
```


Note the variance calculation to get error bars on MSE still needs to be updated.
```{r}
prop_cutoff <- 1
sd_v1 <- 10
c <- 0.4

# create test data frame with v1 for computing density weights later
v <- seq(-30, 30, .01)
test <- tibble(
  v1 = v
)

n_test <- nrow(test)

fl <- list.files(results_folder)
setwd(results_folder)
#res <- dplyr::bind_rows(lapply(fl, readRDS))

res1 <- dplyr::bind_rows(lapply(fl[1:250], readRDS)) %>% dplyr::filter(eps_sd_pi != 5)
res2 <- dplyr::bind_rows(lapply(fl[251:500], readRDS)) %>% dplyr::filter(eps_sd_pi != 5)

res <- rbind(res1, res2)
rm(res1, res2)

res %>%
  dplyr::group_by(eps_n_exp, eps_sd_mu, eps_sd_pi, method, nu, v1) %>%
  dplyr::summarise(variance = var(pred),
                   bias = mean(pred) - mean(nu),
                   pred = mean(pred)
                   ) -> res_agg

total_w <- sum(dnorm(test$v1, mean = 0, sd = sd_v1))
res_agg %>% 
  dplyr::mutate(sqerr = bias^2 + variance,
    w = dnorm(v1, mean = 0, sd = sd_v1)/total_w) -> res_agg

res_agg %>% 
  dplyr::ungroup() %>%
  dplyr::group_by(eps_n_exp, eps_sd_mu, eps_sd_pi, method) %>%
  dplyr::summarise(mse = sum(w*sqerr),
                vse = n_test * var(w*sqerr)) %>%
  dplyr::mutate(low = mse - 1.96 *sqrt(vse),
                high = mse + 1.96 *sqrt(vse)
                )-> res_sum
```


> visualize predictions and true values for a given simulation

```{r}
res %>%
  dplyr::filter(sim_num < 6, eps_sd_mu == 5, eps_n_exp == 0.25) %>%
  tidyr::pivot_wider(names_from = method, values_from = pred) %>%
  tidyr::pivot_longer(cols = c(nu, pl:bct), names_to = "method", values_to = "pred") %>%
  ggplot(aes(x = v1, y = pred, color = method)) + geom_point(size = 0.3) + facet_grid(sim_num ~. ) + ylim(c(0, 1.5))
  
```


> check that weights are 1 

```{r}
res_agg %>% 
  dplyr::filter(method == "pl", eps_sd_mu == 5, eps_n_exp == .1) %>% 
  dplyr::pull(w) %>% sum()
```


> compute MSE. We see roughly the expected behavior. We could plot more points in between [0.25, 0.5]. Note that we don't see a crossing exactly at 0.25 likely because of constants. 

```{r}
res_sum %>%
  #dplyr::filter(method != "bc") %>%
    ggplot(aes(x=eps_n_exp, y= mse, color = method, fill = method))  +
  geom_ribbon(aes(ymin=low, ymax=high), alpha = 0.4) + 
  geom_point() + 
  ylab('Mean Squared Error') + 
  facet_grid(eps_sd_mu ~ eps_sd_pi)  + 
  theme_grey(base_size=12)    + theme(legend.position = "bottom") 
#ggsave("img/mse.pdf")
```

> compute MSE for 1) noisy regression and 2) bias-corrected using noisy propensity and noisy regression

```{r}
res_sum %>%
  dplyr::filter(method != "bct") %>%
    ggplot(aes(x=eps_n_exp, y= mse, color = method, fill = method))  +
  geom_ribbon(aes(ymin=low, ymax=high), alpha = 0.4) + 
  geom_point() + 
  ylab('Mean Squared Error') + 
  facet_grid(eps_sd_mu ~ eps_sd_pi)  + 
  theme_grey(base_size=12)    + theme(legend.position = "bottom") 
#ggsave("img/mse.pdf")
```



```{r}
res_agg %>%
  dplyr::filter(eps_n_exp == .25, method != "bc") %>%
   ggplot(aes(x = v1, y = bias^2, color = method, fill = method)) + geom_point(size = 0.25) + facet_grid(eps_sd_mu ~.)  + theme_grey(base_size=12)    + theme(legend.position = "bottom") 

#ggsave("img/sq_bias.pdf")
```

```{r}
res_agg %>%
  #dplyr::filter(eps_n_exp == .1, method != "bc") %>%
   ggplot(aes(x = v1, y = variance, color = method, fill = method)) + geom_point(size = 0.25) + facet_grid(eps_sd_mu ~.)  + theme_grey(base_size=12)    + theme(legend.position = "bottom") 

#ggsave("img/var.pdf")
```

> Mean predicitons by true regression value
> shows the bias in the plugin

```{r}
res_agg %>%
  dplyr::filter(eps_n_exp == .005) %>%
   ggplot(aes(x = nu, y = pred, color = method, fill = method)) + geom_point()+ geom_abline(slope= 1, intercept = 0)  + facet_grid(eps_sd_mu ~.)  + theme_grey(base_size=12)    + theme(legend.position = "bottom") 
```

```{r}
res_agg %>%
  dplyr::filter(eps_n_exp == .1) %>%
   ggplot(aes(x = nu, y = pred, color = method, fill = method)) + geom_point(size = 0.25)+ geom_abline(slope= 1, intercept = 0)  + facet_grid(eps_sd_mu~.)  + theme_grey(base_size=12)    + theme(legend.position = "bottom") 
```

```{r}
res_sum %>%
  dplyr::filter(eps_n_exp == 0.1)
```

> Performance at the mean covariate v1 = 0

```{r}
res_agg %>%
  dplyr::filter(v1 == 0) %>% 
   ggplot(aes(x=eps_n_exp, y= sqerr, color = method, fill = method)) + geom_point()+ ylab('Mean Squared Error') + facet_grid(eps_sd_mu ~.)  + theme_grey(base_size=12)    + theme(legend.position = "bottom") 

```

