---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(latex2exp)
source("plot_utils.R")
```

```{r}
# binary
results_folder <- "results/highdim/errordistr/"

# regression
#results_folder <- "results/highdim/regression/prop_widen/calib/"
results <- readRDS(glue::glue(results_folder, "results.Rds"))

# to save images
#img_folder <- "img/regression_"
img_folder <- "img/binary_"
```

```{r}
results %>%
  dplyr::select(-bct) %>%
  pivot_longer(cols = bc:conf, names_to = "method", values_to = "prediction") %>%
  dplyr::mutate(method = factor(recode(method,
    bc = "DR",
    conf = "BTR",
    pl = "PL"
  ),
  levels = rev(c(
    "DR",
    "PL",
    "BTR"
  ))
  )) -> results
```


# Fixed bin count (quantiles), variable bin width
```{r}
num_bin <- 20
```


> errors against mu

```{r} 
results %>%
  group_by(method) %>%
  mutate(
    b = ntile(mu0, num_bin),
    abs_err = abs(nu - prediction)^2
  ) %>%
  group_by(method, b) %>%
  summarise(
    mean_err = mean(abs_err),
    mean_mu = mean(mu0),
    low = mean(abs_err) - 1.96 * sqrt(var(abs_err) / n()),
    high = mean(abs_err) + 1.96 * sqrt(var(abs_err) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_mu, y = mean_err, color = method)) +
  geom_point() +
  theme_bw() +
  scale_color_manual(values = cbPalette[1:3]) +
  ylab(TeX("$(\\nu(V) - \\hat{\\nu}(V))^2$")) +
  xlab(TeX("$\\mu(V,Z)$")) +
  geom_errorbar(aes(ymin = low, ymax = high))
 ggsave(glue::glue(img_folder, "errors_mu.pdf"))
```


>  errors against nu

```{r} 
results %>%
  group_by(method) %>%
  mutate(
    b = ntile(nu, num_bin),
    abs_err = abs(nu - prediction)^2
  ) %>%
  group_by(method, b) %>%
  summarise(
    mean_err = mean(abs_err),
    mean_nu = mean(nu),
    low = mean(abs_err) - 1.96 * sqrt(var(abs_err) / n()),
    high = mean(abs_err) + 1.96 * sqrt(var(abs_err) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_nu, y = mean_err, color = method)) +
  geom_point() +
  theme_bw() +
  scale_color_manual(values = cbPalette[1:3]) +
  ylab(TeX("$(\\nu(V) - \\hat{\\nu}(V))^2$")) +
  xlab(TeX("$\\nu(V)$")) +
  geom_errorbar(aes(ymin = low, ymax = high))
 ggsave(glue::glue(img_folder, "errors_nu.pdf"), width = 10, height = 8)
```

# errors against propensities
```{r} 
results %>%
  group_by(method) %>%
  mutate(
    b = ntile(prop, num_bin),
    abs_err = abs(nu - prediction)^2
  ) %>%
  group_by(method, b) %>%
  summarise(
    mean_err = mean(abs_err),
    mean_pi = mean(prop),
    low = mean(abs_err) - 1.96 * sqrt(var(abs_err) / n()),
    high = mean(abs_err) + 1.96 * sqrt(var(abs_err) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_pi, y = mean_err, color = method)) +
  geom_point() +
  theme_bw() +
  scale_color_manual(values = cbPalette[1:3]) +
  ylab(TeX("$(\\nu(V) - \\hat{\\nu}(V))^2$")) +
  xlab(TeX("$\\pi(V,Z)$")) +
  geom_errorbar(aes(ymin = low, ymax = high))
 ggsave(glue::glue(img_folder, "errors_pi.pdf"), width = 10, height = 8)
```

# reverse calibration 
```{r} 
results %>%
  group_by(method) %>%
  mutate(b = ntile(nu, num_bin)) %>%
  group_by(method, b) %>%
  summarise(
    mean_pred = mean(prediction),
    mean_nu = mean(nu),
    low_pred = mean(prediction) - 1.96 * sqrt(var(prediction) / n()),
    high_pred = mean(prediction) + 1.96 * sqrt(var(prediction) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_nu, y = mean_pred, color = method)) +
  geom_point() +
  geom_errorbar(aes(ymin = low_pred, ymax = high_pred)) +
  geom_abline(linetype = "dashed", color = "grey") +
  scale_color_manual(values = cbPalette[1:3]) +
  ylab(TeX("$\\hat{\\nu}(V)$")) +
  xlab(TeX("$\\nu(V)$")) +
  theme_bw() + 
  coord_fixed()
 ggsave(glue::glue(img_folder, "inv_cali.pdf"))
```

> calibration
note the error bars are too small to be legible (can see if you increase bin to 500 and decrease size of point to 0.1)

```{r} 
results %>%
  # filter(sim ==5 ) %>%
  group_by(method) %>%
  mutate(b = ntile(prediction, num_bin)) %>%
  group_by(method, b) %>%
  summarise(
    mean_pred = mean(prediction),
    mean_nu = mean(nu),
    low_nu = mean(nu) - 1.96 * sqrt(var(nu) / n()),
    high_nu = mean(nu) + 1.96 * sqrt(var(nu) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_pred, y = mean_nu, color = method)) +
  geom_point() +
  geom_errorbar(aes(ymin = low_nu, ymax = high_nu)) +
  scale_color_manual(values = cbPalette[1:3]) +
  geom_abline(linetype = "dashed", color = "grey") +
  xlab(TeX("$\\hat{\\nu}(V)$")) +
  ylab(TeX("$\\nu(V)$")) +
  theme_bw() +
  coord_fixed()
 ggsave(glue::glue(img_folder, "calib.pdf"), width = 10, height = 8)
```


# Fixed bin width, variable bin count

# errors against mu
```{r} 
results %>%
  mutate(
    mu_bin = round(mu0),
    abs_err = abs(nu - prediction)
  ) %>%
  group_by(method, mu_bin) %>%
  summarise(
    mean_err = mean(abs_err),
    mean_mu = mean(mu0),
    low = mean(abs_err) - 1.96 * sqrt(var(abs_err) / n()),
    high = mean(abs_err) + 1.96 * sqrt(var(abs_err) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_mu, y = mean_err, color = method)) +
  scale_color_manual(values = cbPalette[1:3]) +
  geom_point() +
  geom_errorbar(aes(ymin = low, ymax = high))
# ggsave("img/binary_calibration_multi_sim.pdf")
```

# errors against nu
```{r} 
results %>%
  mutate(
    nu_bin = round(nu),
    abs_err = abs(nu - prediction)
  ) %>%
  group_by(method, nu_bin) %>%
  summarise(
    mean_err = mean(abs_err),
    mean_nu = mean(nu),
    low = mean(abs_err) - 1.96 * sqrt(var(abs_err) / n()),
    high = mean(abs_err) + 1.96 * sqrt(var(abs_err) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_nu, y = mean_err, color = method)) +
  geom_point() +
  scale_color_manual(values = cbPalette[1:3]) +
  geom_errorbar(aes(ymin = low, ymax = high))
# ggsave("img/binary_calibration_multi_sim.pdf")
```

# errors against propensities
```{r} 
results %>%
  mutate(
    pi_bin = round(prop * 10),
    abs_err = abs(nu - prediction)
  ) %>%
  group_by(method, pi_bin) %>%
  summarise(
    mean_err = mean(abs_err),
    mean_pi = mean(prop),
    low = mean(abs_err) - 1.96 * sqrt(var(abs_err) / n()),
    high = mean(abs_err) + 1.96 * sqrt(var(abs_err) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_pi, y = mean_err, color = method)) +
  geom_point() +
  scale_color_manual(values = cbPalette[1:3]) +
  geom_errorbar(aes(ymin = low, ymax = high))
# ggsave("img/binary_calibration_multi_sim.pdf")
```

# reverse calibration 
```{r} 
results %>%
  # mutate(nu_bin = round(nu*10)) %>%
  mutate(nu_bin = round(nu)) %>%
  group_by(method, nu_bin) %>%
  summarise(
    mean_pred = mean(prediction),
    mean_nu = mean(nu),
    low_pred = mean(prediction) - 1.96 * sqrt(var(prediction) / n()),
    high_pred = mean(prediction) + 1.96 * sqrt(var(prediction) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_nu, y = mean_pred, color = method)) +
  geom_point() +
  geom_errorbar(aes(ymin = low_pred, ymax = high_pred)) +
  scale_color_manual(values = cbPalette[1:3]) +
  geom_abline()
# ggsave("img/binary_calibration_multi_sim.pdf")
```

# calibration 
```{r} 
results %>%
  # filter(sim ==5 ) %>%
  mutate(pred_bin = round(prediction / 2)) %>%
  group_by(method, pred_bin) %>%
  summarise(
    mean_pred = mean(prediction),
    mean_nu = mean(nu),
    low_nu = mean(nu) - 1.96 * sqrt(var(nu) / n()),
    high_nu = mean(nu) + 1.96 * sqrt(var(nu) / n())
  ) %>%
  ggplot(mapping = aes(x = mean_pred, y = mean_nu, color = method)) +
  geom_point() +
  geom_errorbar(aes(ymin = low_nu, ymax = high_nu)) +
  scale_color_manual(values = cbPalette[1:3]) +
  geom_abline()
# ggsave("img/binary_calibration_multi_sim.pdf")
```
