---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(latex2exp)
source("plot_utils.R")
```

```{r}
# regression
results_folder <- "results/highdim/regression/prop_widen/eval/p300/p300"
results <- readRDS(glue::glue(results_folder, "results.Rds"))

# to save images
img_folder <- "img/regression_"
```

```{r}
results %>%
  dplyr::filter(eval %in% c("true_reg_mse", "true_pred_mse", "dr_observational")) %>%
  dplyr::group_by(eval, method) %>%
  dplyr::summarise(
    mmse = mean(mse),
    count = n(),
    vmse = var(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()), 
  ) 
```

> plot averages against each other

```{r}
results %>%
  dplyr::filter(eval %in% c("true_reg_mse", "dr_observational")) %>%
  dplyr::group_by(eval, method) %>%
  dplyr::summarise(
    mmse = mean(mse),
    count = n(),
    vmse = var(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()), 
  ) %>%
  dplyr::select(-vmse, -low, -high, -count) %>%
  tidyr::pivot_wider(names_from = eval, values_from = mmse) %>%
  ggplot(aes(x = true_reg_mse, y = dr_observational, color = method)) +
  geom_point() +
  theme_bw(base_size = 18)
ggsave("img/obs_eval_avg.pdf")
```

```{r}
results %>%
  dplyr::filter(eval %in% c("true_pred_mse", "dr_observational")) %>%
  dplyr::group_by(eval, method) %>%
  dplyr::summarise(
    mmse = mean(mse),
    count = n(),
    vmse = var(mse),
    low = mean(mse) - 1.96 * sqrt(var(mse) / n()),
    high = mean(mse) + 1.96 * sqrt(var(mse) / n()), 
  ) %>%
  dplyr::select(-vmse, -low, -high, -count) %>%
  tidyr::pivot_wider(names_from = eval, values_from = mmse) %>%
  ggplot(aes(x = true_pred_mse, y = dr_observational, color = method)) +
  geom_point() +
  theme_bw(base_size = 18) +
  ggsave("img/obs_eval_pred.pdf")
```

> show percentage of simulations in which the orders were the same for dr and true_reg

```{r}
results %>%
  group_by(sim, eval) %>%
  mutate(rnk = min_rank(mse))%>%
  ungroup() %>%
  group_by(sim, method) %>%
  filter(eval %in% c("true_reg_mse", "dr_observational")) %>%
  select(mse, method, eval, sim, rnk) %>%  
  summarise(discr = var(rnk)) %>%
  ungroup() %>%
  group_by(sim) %>%
  summarise(discr_sim = as.integer(max(discr) >0)) %>%
  summary()

```

> show percentage of simulations in which the orders were the same for dr and true_pred

```{r}
results %>%
  select(mse, method, eval, sim) %>%  
  group_by(sim, eval) %>%
  mutate(rnk = min_rank(mse)) %>%
  ungroup() %>%
  group_by(sim, method) %>%
  filter(eval %in% c("true_pred_mse", "dr_observational")) %>%
  summarise(discr = var(rnk)) %>%
  ungroup() %>%
  group_by(sim) %>%
  summarise(discr_sim = as.integer(max(discr) >0)) %>%
  summary()

```

> show percentage of simulations in which rank 1 was the same for dr and true_reg

```{r}
results %>%
  select(mse, method, eval, sim) %>%  
  group_by(sim, eval) %>%
  mutate(rnk = min_rank(mse))%>%
  ungroup() %>%
  group_by(sim) %>%
  filter(eval %in% c("true_reg_mse", "dr_observational"),
         rnk == 1) %>%
  mutate(same = as.integer(first(method) == last(method))) %>%
  ungroup() %>%
  group_by(sim) %>%
  summary()

```


> show percentage of simulations in which rank 1 was the same for dr and true_pred

```{r}
results %>%
  select(mse, method, eval, sim) %>%  
  group_by(sim, eval) %>%
  mutate(rnk = min_rank(mse))%>%
  ungroup() %>%
  group_by(sim) %>%
  filter(eval %in% c("true_pred_mse", "dr_observational"),
         rnk == 1) %>%
  mutate(same = as.integer(first(method) == last(method))) %>%
  ungroup() %>%
  group_by(sim) %>%
  summary()

```


>  compare: show percentage of simulations in which rank 1 was the same for true_reg and true_pred

```{r}
results %>%
  select(mse, method, eval, sim) %>%  
  group_by(sim, eval) %>%
  mutate(rnk = min_rank(mse))%>%
  ungroup() %>%
  group_by(sim) %>%
  filter(eval %in% c("true_pred_mse", "true_reg_mse"),
         rnk == 1) %>%
  mutate(same = as.integer(first(method) == last(method))) %>%
  ungroup() %>%
  group_by(sim) %>%
  summary()

```

```{r}
results %>%
  dplyr::filter(eval %in% c("true_reg_mse", "true_pred_mse", "dr_observational")) %>%
  dplyr::filter(sim == 35)
```

